---
title: "`r params$report_title`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
params:
  report_title: NA
  # Misc. stuff (file names/ user-specified names;)
  filename_TLStest: NA      #fn TLS data under test
  filename_reflengths: NA   #fn Reference Lengths
  dataname_test: NA         #user-name for TLS data under test
  
  ## Part I stuff
  length_summary: NA
  error_plot: NA
  error_table: NA
  lengtherror_statements: NA
  
  ## MCS stuff
  expected_errors: NA
  expectederrors_summary: NA
  expectederror_plot: NA
  seed_value: NA
  nIt_mcs: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Part I Summary
`r params$length_summary`

<!-- PART I ERROR PLOT -->
```{r, echo=FALSE, fig.width=8, fig.height=3.75, fig.align='center', out.width="80%"}
if (!is.null(params$error_plot)) {
  params$error_plot
}
```
### Part II Summary
`r params$expectederrors_summary`

<!-- EXPECTED ERRORS FROM MCS -->
```{r, echo=FALSE, fig.width=8, fig.height=3.75, fig.align='center', out.width="80%"}
if (!is.null(params$expectederror_plot)) {
  params$expectederror_plot
}
```

### Part I - Details on the six lengths and their reference values
```{r, echo=FALSE, results='asis'}
if (!is.null(params$lengtherror_statements)) {
  for (item in params$lengtherror_statements$statement) {
    cat("* ", item, "\n")
  }
} else {
  "No statement data available."
}
```

### Part I - Complete Table of Errors
<!-- 1. 'params$error_table' is the data you sent from the app-->
<!-- 2. 'knitr::kable()' turns that data into a pretty table for PDF-->
```{r, echo=FALSE}
if (!is.null(params$error_table)) {
  knitr::kable(params$error_table, 
               caption = "Part I Length Errors",
               booktabs = TRUE) 
} else {
  "No table data available."
}
```
### Part II - Complete Table
<!-- EXPECTED ERRORS FROM MCS -->
```{r, echo=FALSE}
if (!is.null(params$expected_errors)) {
  knitr::kable(params$expected_errors, 
               caption = "Part II MCS Results",
               booktabs = TRUE) 
} else {
  "No table data available."
}
```
These results were obtained from a Monte Carlo simulation using `r params$nIt_mcs` iterations and may be replicated 
using the seed `r params$seed_value`.

### Data Summaries

'`r params$dataname_test`' data read from file `r params$filename_TLStest`. Reference lengths corresponding to these data were read from file `r params$filename_reflengths`.