---
title: "`r params$report_title`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
header-includes:
#  - \usepackage{tcolorbox}
params:
  report_title: NA
  
  # Misc. stuff (file names/ user-specified names;)
  ## CURRENT DATA
  ##   TLS data - meta
  filename_TLStest: NA      #fn TLS data under test
  dataname_test: NA         #user-specified nickname for TLS data under test
  nT_test: NA
  nP_test: NA
  TLS_UnitStatement: NA
  ##    Reference Length data
  filename_reflengths: NA   #fn Reference Lengths
  tapedata_summary: NA      #units for Reference Lengths (current)
  ##
  ## HISTORIC DATA
  ##    TLS data
  filename_TLShist: NA      #fn for historic TLS data
  dataname_base: NA         #user-specified nickname for Historic TLS data
  nT_base: NA               #number of targets in Historic TLS data
  nP_base: NA               #number of positions in Historic TLS data
  historicTLS_UnitStatement: NA #unit statement for historic TLS data
  ##    Reference Length data
  
  ## Part I stuff
  length_summary: NA
  error_plot: NA
  error_table: NA
  lengtherror_statements: NA
  
  ## Part II stuff
  sd_test: NA
  sigmaHat_test: NA
  
  ## MCS stuff
  expected_errors: NA
  expectederrors_summary: NA
  expectederror_plot: NA
  seed_value: NA
  nIt_mcs: NA
  
  ## Data summaries/Notes
  notes: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, echo=FALSE, results='asis'}
if (!is.null(params$notes) && nchar(trimws(params$notes)) > 0) {
  # 1. Escape special LaTeX characters first so they don't crash the PDF
  # This handles: %, $, &, #, _, { }
  safe_notes <- gsub("([#$%&_{}])", "\\\\\\1", params$notes)
  
  # 2. Convert manual line breaks (\n) into LaTeX paragraph breaks (\par)
  safe_notes <- gsub("\n", "\\\\par\n", safe_notes)
  
  # 3. Render the block
  cat("\n\\hrule\n") 
  cat("\\vspace{5pt}\n")
  cat("\\textbf{Report Notes:}\n")
  
  cat("\\begin{quote}\n")
  cat("\\small\\ttfamily\n") # Small, monospaced font
  cat(safe_notes)
  cat("\n\\end{quote}\n")
  
  cat("\\hrule\n")
  cat("\\vspace{10pt}\n")
} else {
  cat("\\textit{No notes provided.}")
}
```

## SUMMARY
### Part I Summary
`r params$length_summary`

<!-- PART I ERROR PLOT -->
```{r, echo=FALSE, fig.width=8, fig.height=3.75, fig.align='center', out.width="80%"}
if (!is.null(params$error_plot)) {
  params$error_plot
}
```
### Part II Summary
```{r, echo=FALSE, results='asis'}
if (!is.null(params$sd_test)) {
  # 1. Convert the HTML object to a character string
  sdtest_string <- as.character(params$sd_test)
  
  # 2. Replace <br> tags with LaTeX line breaks
  # We use quadruple backslashes because R escapes them for LaTeX
  sdtest_string_clean <- gsub("<br\\s*/?>", "\\\\par\n", sdtest_string)
  
  # 3. Clean up any other potential HTML artifacts
  sdtest_string_clean <- gsub("<.*?>", "", sdtest_string_clean) 
  
  # 4. Print to PDF
  cat(sdtest_string_clean)
}
```



`r params$expectederrors_summary`

<!-- EXPECTED ERRORS FROM MCS -->
```{r, echo=FALSE, fig.width=8, fig.height=3.75, fig.align='center', out.width="80%"}
if (!is.null(params$expectederror_plot)) {
  params$expectederror_plot
}
```

### Part I - Details on the six lengths and their reference values
```{r, echo=FALSE, results='asis'}
if (!is.null(params$lengtherror_statements)) {
  for (item in params$lengtherror_statements$statement) {
    cat("* ", item, "\n")
  }
} else {
  "No statement data available."
}
```

### Part I - Complete Table of Errors
<!-- 1. 'params$error_table' is the data you sent from the app-->
<!-- 2. 'knitr::kable()' turns that data into a pretty table for PDF-->
```{r, echo=FALSE}
if (!is.null(params$error_table)) {
  knitr::kable(params$error_table, 
               caption = "Part I Length Errors",
               booktabs = TRUE) 
} else {
  "No table data available."
}
```
### Part II - Complete Table
<!-- EXPECTED ERRORS FROM MCS -->
```{r, echo=FALSE}
if (!is.null(params$expected_errors)) {
  knitr::kable(params$expected_errors, 
               caption = "Part II MCS Results",
               booktabs = TRUE) 
} else {
  "No table data available."
}
```
These results were obtained from a Monte Carlo simulation using `r params$nIt_mcs` iterations and may be replicated 
using the seed `r params$seed_value`.

### Current Data Summary
#### TLS Data 
* **filename:** `r params$filename_TLStest`
* **nickname:** `r params$dataname_test`
* **# of targets:** `r params$nT_test`
* **# of positions:** `r params$nP_test`
* **units:** `r params$TLS_UnitStatement`

#### Reference Lengths 
* **filename:** `r params$filename_reflengths`
* **units:** `r params$tapedata_summary`

```{r, echo=FALSE, results='asis'}
# Check if a filename exists for the historic data
if (!is.null(params$filename_TLShist) && params$filename_TLShist != "") {
  
  cat("### Historic Data Summary\n")
  cat("#### TLS Data\n")
  
  # We use a list format
  cat("* **filename:**", params$filename_TLShist, "\n")
  cat("* **nickname:**", params$dataname_base, "\n")
  cat("* **# of targets:**", params$nT_base, "\n")
  cat("* **# of positions:**", params$nP_base, "\n")
  cat("* **units:**", params$historicTLS_UnitStatement, "\n")
  # Add a final newline to separate this from whatever comes next
  cat("\n")
}
```

<!-- '`r params$dataname_test`' data read from file `r params$filename_TLStest`. Reference lengths corresponding to these data were read from file `r params$filename_reflengths`. -->