---
title: "`r params$report_title`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  pdf_document:
    extra_dependencies: ["float", "tcolorbox", "xcolor"]
header-includes:
  - \usepackage{tcolorbox}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \definecolor{profGreen}{HTML}{2E6F40}
  - \definecolor{profGreenBg}{HTML}{F4F8F5}
  - \definecolor{profOrange}{HTML}{D97706}
  - \definecolor{profOrangeBg}{HTML}{FFFBEB}
  - \definecolor{profRed}{HTML}{B91C1C}
  - \definecolor{profRedBg}{HTML}{FEF2F2}
params:
  report_title: NA
  
  # Assessment Context
  assessment_type: NA
  overall_label: NA
  overall_desc: NA
  overall_action: NA
  partI_status: NA
  partII_htest: NA
  partII_eer: NA
  
  # DATA UNDER TEST (Baseline if Baseline Track; Verification if Verification Track)
  has_baseline_comp: NA      
  filename_TLS_test: NA      
  dataname_test: NA          
  nT_test: NA                
  nP_test: NA                
  TLS_UnitStatement: NA      
  filename_reflengths: NA    
  tapedata_summary: NA       
  
  # BASELINE COMPARISON DATA (Only populated/used during Verification track)
  filename_TLS_baseline: NA       
  dataname_baseline: NA           
  nT_baseline: NA                 
  nP_baseline: NA                 
  baseline_TLS_UnitStatement: NA  
  filename_reflengths_baseline: NA
  reflengths_baseline_summary: NA 
  
  # PART I RESULTS (ACCURACY)
  length_summary: NA
  error_plot: NA                
  error_table: NA                
  error_table_sub: NA            
  lengtherror_statements: NA
  mpe_value: NA
  unc_ref: NA
  
  # Baseline Reference Accuracy (Verification track only)
  length_summary_baseline: NA   
  error_table_baseline: NA      
  error_table_sub_baseline: NA  
  error_plot_baseline: NA        
  lengtherror_statements_baseline: NA
  
  # PART II RESULTS (PRECISION)
  sd_test: NA
  sigmaHat_test: NA               
  sigmaHat_baseline: NA           
  baseline_data_sd: NA            
  
  # Precision Comparison & Simulations
  p2_interpretation: NA
  Htest_details: NA               
  ellipse_plot_path: NA           
  expectederrors_summary: NA
  expectederror_plot: NA          
  seed_value: NA                  
  nIt_mcs: NA                     
  expected_errors: NA
  alpha: NA
  
  # Residual Plots
  notes: NA                        
  resPlot_current: NA              
  resPlot_baseline: NA            
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)

# Global helper to map any compliance status string to its professional colors
get_status_colors <- function(status_string) {
  clean_status <- tolower(trimws(status_string))
  
  if (grepl("non-compliant", clean_status, fixed = TRUE)) {
    list(frame = "profRed", back = "profRedBg")
  } else if (grepl("marginally", clean_status, fixed = TRUE)) {
    list(frame = "profOrange", back = "profOrangeBg")
  } else {
    # Default fallback for Compliant states
    list(frame = "profGreen", back = "profGreenBg")
  }
}
```

```{r, echo=FALSE, results='asis'}
if (!is.null(params$notes) && nchar(trimws(params$notes)) > 0) {
  # 1. Escape special LaTeX characters first so they don't crash the PDF
  # This handles: %, $, &, #, _, { }
  safe_notes <- gsub("([#$%&_{}])", "\\\\\\1", params$notes)
  
  # 2. Convert manual line breaks (\n) into LaTeX paragraph breaks (\par)
  safe_notes <- gsub("\n", "\\\\par\n", safe_notes)
  
  # 3. Render the block
  cat("\n\\hrule\n") 
  cat("\\vspace{5pt}\n")
  cat("\\textbf{Report Notes:}\n")
  
  cat("\\begin{quote}\n")
  cat("\\small\\ttfamily\n") # Small, monospaced font
  cat(safe_notes)
  cat("\n\\end{quote}\n")
  
  cat("\\hrule\n")
  cat("\\vspace{10pt}\n")
} else {
  cat("\n\\hrule\n") 
  cat("\\vspace{5pt}\n")
  cat("\\textbf{Report Notes:}\n")
  
  cat("\\textit{No notes provided.}")
  
  cat("\\hrule\n")
  cat("\\vspace{10pt}\n")
}
```

# REPORT SUMMARY

```{r, echo = FALSE, results = 'asis'}
col_frame <- "profGreen"
col_back  <- "profGreenBg"
outcome_str <- tolower(trimws(params$overall_label))

if (grepl("non-compliant", outcome_str, fixed = TRUE)) {
  col_frame <- "profRed"
  col_back  <- "profRedBg"
} else if (grepl("marginally compliant", outcome_str, fixed = TRUE)) {
  col_frame <- "profOrange"
  col_back  <- "profOrangeBg"
}

# Standardize the assessment type string to uppercase
asmt_type <- toupper(trimws(params$assessment_type))
# If the parameter is just "BASELINE" or "VERIFICATION", append "ASSESSMENT"
if (!grepl("ASSESSMENT", asmt_type, fixed = TRUE)) {
  asmt_type <- paste(asmt_type, "ASSESSMENT")}
# Dynamically combine the type and the outcome string
box_title <- sprintf("%s - %s", asmt_type, params$overall_label)

cat(sprintf("\\begin{tcolorbox}[colframe=%s, colback=%s, title=\\textbf{%s}, sharp corners=west, arc=4pt, boxrule=2pt, left=12pt, right=12pt]", 
            col_frame, col_back, box_title))
cat("\n\\begin{itemize}\n")
cat(sprintf("  \\item \\textbf{Part I Accuracy Evaluation:} %s\n", params$partI_status))
cat(sprintf("  \\item \\textbf{Part II Spherical Precision Hypothesis Test:} %s\n", params$partII_htest))
cat(sprintf("  \\item \\textbf{Part II Expected Error Range (EER) Simulation:} %s\n", params$partII_eer))
cat("\\end{itemize}\n")
cat("\\vspace{5pt}\n")
cat(sprintf("\\noindent\\textbf{Finding Statement:} %s\\par\n", params$overall_desc))
cat("\\vspace{5pt}\n")
cat(sprintf("\\noindent\\textbf{Recommendation:} %s\n", params$overall_action))
cat("\\end{tcolorbox}\n")
```

\vspace{10pt}
\noindent\rule{\textwidth}{0.4pt}

# EVALUATION DETAILS

## Part I - Target-to-Target Accuracy

```{r, echo=FALSE, results='asis'}
# Fetch the colors from the global helper
colors <- get_status_colors(params$partI_status)

# Format the display strings for the threshold and uncertainty values
# (Ensure 'unc_ref' and 'mpe_value' are passed into your params list from Shiny)
mpe_display <- if (!is.null(params$mpe_value)) paste(params$mpe_value, "mm") else "[Not Specified]"
unc_ref_display <- if (!is.null(params$unc_ref)) paste(params$unc_ref, "mm") else "[Not Specified]"

desc_text <- if (params$partI_status == "COMPLIANT") {
  sprintf("All 24 length errors are less than the specified MPE of %s. Instrument accuracy is within specifications.", mpe_display)
} else {
  sprintf("At least one of the 24 length errors exceeds the specified MPE of %s. Instrument accuracy does not meet specifications.", mpe_display)
}

# Render the box with the explicit evaluation metrics cleanly stacked
cat(sprintf("\\begin{tcolorbox}[colframe=%s, colback=%s, sharp corners, boxrule=1pt, left=10pt, right=10pt, top=8pt, bottom=8pt]", 
            colors$frame, colors$back))

cat(sprintf("\\textbf{Part I Status Evaluation: %s}\\par\\vspace{4pt}\n", params$partI_status))
cat(sprintf("\\noindent\\small\\textbf{Evaluation Threshold (MPE):} %s\\par\\vspace{2pt}\n", mpe_display))
cat(sprintf("\\noindent\\small\\textbf{Reference Length Uncertainty:} %s\\par\\vspace{4pt}\n", unc_ref_display))
cat(sprintf("\\noindent\\small\\textbf{Analysis Finding:} %s\n", desc_text))

cat("\\end{tcolorbox}\n")
cat("\\vspace{5pt}\n")
# Replicate the Shiny app warning logic inside the PDF report
if (!is.null(params$unc_ref) && params$unc_ref < 1) {
  cat("\\vspace{4pt}\n")
  cat("\\begin{tcolorbox}[colframe=profOrange, colback=profOrangeBg, sharp corners, boxrule=1pt, left=10pt, right=10pt, top=6pt, bottom=6pt]\n")
  cat("\\small\\textbf{Documentation Required:} You will need formal documentation to support using a reference length uncertainty value this low.\n")
  cat("\\end{tcolorbox}\n")
}
```

```{r, echo = FALSE, results = 'asis'}
## display any errors that exceed the MPE, if applicable
if (is.data.frame(params$error_table_sub) && nrow(params$error_table_sub) > 0) {
  cat("Units in table are mm.\n")
  print(knitr::kable(params$error_table_sub, 
                     caption = "Length errors that exceed the given MPE",  
                     booktabs = TRUE))
  cat("\n\n") 
}
```






## Part II - Spherical Precision

```{r, echo=FALSE, results='asis'}
# 1. Standardize incoming parameter strings
h_status <- toupper(trimws(params$partII_htest))
e_status <- toupper(trimws(params$partII_eer))

# 2. Determine the overall color profile based on the worst-case sub-status
if (e_status == "NON-COMPLIANT") {
  # Critical failure safeguard: Red box
  colors <- get_status_colors("NON-COMPLIANT")
} else if (h_status == "NON-COMPLIANT") {
  # Your rule: Hypothesis Test is Non-Compliant -> Orange box
  colors <- get_status_colors("MARGINALLY COMPLIANT")
} else if (h_status == "N/A") {
  # Baseline track fallback -> Gray box
  colors <- list(frame = "gray!60", back = "gray!5")
} else {
  # Your rule: Hypothesis Test is Compliant -> Green box
  colors <- get_status_colors("COMPLIANT")
}

# 3. Map out the descriptive narrative text for the Hypothesis Test
h_desc <- if (h_status == "COMPLIANT") {
  "There has not been a statistically significant change in instrument precision."
} else if (h_status == "NON-COMPLIANT") {
  "A statistically significant change in the instrument's spherical precision has been detected."
} else {
  "Part II has no compliance assessment during a Baseline Evaluation. Only the standard deviation in the spherical residuals are reported."
}

# 4. Map out the descriptive narrative text for the Monte Carlo EER Simulation
e_desc <- if (e_status == "COMPLIANT") {
  sprintf("All 24 EER values are less than the specified MPE of %s.", mpe_display)
} else if (e_status == "NON-COMPLIANT") {
  sprintf("At least one of the 24 EER values exceeds the specified MPE of %s.", mpe_display)
} else {
  "No EER simulation was required."
}

# 5. Render the structured sub-assessment container
cat(sprintf("\\begin{tcolorbox}[colframe=%s, colback=%s, sharp corners, boxrule=1pt, left=10pt, right=10pt, top=8pt, bottom=8pt]", 
            colors$frame, colors$back))

cat("\\textbf{Part II Spherical Precision Evaluation}\\par\\vspace{5pt}\n")

cat(sprintf("\\noindent\\small\\textbf{Hypothesis Test Status:} %s\\par\\vspace{1pt}\n", h_status))
cat(sprintf("\\noindent\\small\\textbf{Test Finding:} %s\\par\\vspace{6pt}\n", h_desc))

cat(sprintf("\\noindent\\small\\textbf{Expected Error Range (EER) Simulation:} %s\\par\\vspace{1pt}\n", e_status))
cat(sprintf("\\noindent\\small\\textbf{Simulation Finding:} %s\n", e_desc))

cat("\\end{tcolorbox}\n")
cat("\\vspace{5pt}\n")

# Give warning if alpha was changed from 0.01
if (!is.null(params$alpha) && params$alpha != 0.01) {
  cat("\\vspace{4pt}\n")
  cat("\\begin{tcolorbox}[colframe=profOrange, colback=profOrangeBg, sharp corners, boxrule=1pt, left=10pt, right=10pt, top=6pt, bottom=6pt]\n")
  cat("\\small\\textbf{Notification:} Statistical significance threshold changed from default value of 0.01.\n")
  cat("\\end{tcolorbox}\n")
}
```


#### Precision - `r params$dataname_test`

```{r, echo=FALSE, results='asis'}
if (!is.null(params$sd_test)) {
  cat("\n\n")
  sdtest_string <- as.character(params$sd_test)
  sdtest_string_clean <- gsub("<br\\s*/?>", "\\\\par\n", sdtest_string)
  sdtest_string_clean <- gsub("<.*?>", "", sdtest_string_clean) 
  cat(sdtest_string_clean)
  cat("\n\n\\par\n\n")
}
```


```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$baseline_data_sd)) {
  cat("### Precision - ", params$dataname_baseline, "\n\n", sep ="")
  cat("The standard deviation in the azimuth angle residuals in the baseline dataset is ", params$baseline_data_sd[1], " arcsec.\\par\n", sep = "")
  cat("The standard deviation in the elevation angle residuals in the baseline dataset is ", params$baseline_data_sd[2], " arcsec.\\par\n", sep = "")
  cat("The historical standard deviation in the ranging residuals in the baseline dataset is ", params$baseline_data_sd[3], " mm\\par\n", sep = "")
  cat("\n\n")
}
```

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$p2_interpretation)) {
  cat("#### Precision Comparison Analysis\n\n")
  cat(params$p2_interpretation)
  cat("\n\n")
}
```

```{r, echo=FALSE, results='asis'}
if(params$has_baseline_comp == "Yes" && !is.null(params$expectederrors_summary)) {
  cat("#### Effect of Current Precision State on Target Dimensions\n\n")
  cat("Since there is a statistically significant change in the precision, the effect of the instrument’s current spherical precision on the length measurements has been estimated using a Monte Carlo simulation. The “expected error range” (EER) value computed from this simulation is the range of error, for a given length and position, that is expected in the instrument’s measurement due to the current spherical precision.\n\n")
  cat(params$expectederrors_summary)
  cat("\n\n")
}
```


\noindent\rule{\textwidth}{0.4pt}
\clearpage

# APPENDIX: DETAILED RESULTS

## Part I: Target-to-Target Accuracy 

### Part I: Plot of Length Errors - `r params$dataname_test`
```{r, echo=FALSE, fig.width=7, fig.height=3.25, fig.align='center', out.width="75%", fig.pos='H', fig.cap="Target-to-Target Length Errors"}
if (!is.null(params$error_plot)) {
  params$error_plot
}
```

### Part I: Complete Table of Length Errors - `r params$dataname_test` (units are mm)
```{r, echo=FALSE, results='asis'}
if (!is.null(params$error_table)) {
  knitr::kable(params$error_table, 
               caption = paste("All 24 Length Errors -", params$dataname_test),
               booktabs = TRUE) 
}
```

\vspace{10pt}

### Part I: Designated Lengths and their Reference Values - `r params$dataname_test`
```{r, echo=FALSE, results='asis'}
if (!is.null(params$lengtherror_statements)) {
  for (item in params$lengtherror_statements$statement) {
    cat("* ", item, "\n")
  }
  cat("\n\n")
}
```

```{r, echo=FALSE, results='asis', fig.width=7, fig.height=3.25, fig.align='center', out.width="75%", fig.pos='H', fig.cap="Target-to-Target Length Errors - Baseline data"}
if (params$has_baseline_comp == 'Yes' && !is.null(params$error_plot_baseline)) {
  cat("### Part I: Plot of Length Errors - Baseline data\n\n")
  print(params$error_plot_baseline)
}
```

```{r, echo = FALSE, results = 'asis'}
## display any errors that exceed the MPE, if applicable
if (params$has_baseline_comp == 'Yes' && is.data.frame(params$error_table_sub_baseline) && nrow(params$error_table_sub_baseline) > 0) {
  cat("Units in table are mm.\n")
  print(knitr::kable(params$error_table_sub_baseline, 
                     caption = "Part I: Baseline length errors that exceed the MPE",  
                     booktabs = TRUE))
  cat("\n\n") 
}
```

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$error_table_baseline)) {
  cat("\n### Part I: Complete Table of Length Errors - Baseline data (units are mm)\n\n")
  print(knitr::kable(params$error_table_baseline, 
                     caption = paste("All 24 Length Errors -", params$dataname_baseline),
                     booktabs = TRUE))
  
  
}
```

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$lengtherror_statements_baseline)) {
  cat("\n### Part I: Designated Lengths and their Reference Values - Baseline data \n\n")
  for (item in params$lengtherror_statements_baseline$statement) {
    cat("* ", item, "\n")
  }
  cat("\n\n")
}
```

\vspace{10pt}

## Part II: Spherical Precision 
### Part II: Estimated covariance matrix (`r params$dataname_test`)
```{r, echo=FALSE}
if (!is.null(params$sigmaHat_test)) {
  print(round(params$sigmaHat_test,3))
}
```

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$sigmaHat_baseline)) {
  cat("### Part II: Estimated Covariance Matrix (Baseline data)\n\n")
  
  # Manually wrap the output in a monospace code fence block
  cat("```\n")
  print(round(params$sigmaHat_baseline, 3))
  cat("```\n\n")
}
```


\vspace{5pt}
\noindent\textbf{Coordinate Definitions:}
\begin{verse}
theta = azimuth angle (arcsec) \\
phi = elevation angle (arcsec) \\
r = ranging direction (mm)
\end{verse}

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$Htest_details)) {
  cat("\n\n### Part II: Statistical Hypothesis Test Details\n\n")
}
```
```{r, echo=FALSE}
if (params$has_baseline_comp == "Yes" && !is.null(params$Htest_details)) {
  print(params$Htest_details)
}
```

```{r, echo=FALSE, fig.align='center', results='asis', fig.width=5.5, fig.height=5.5, out.width="60%", fig.pos='H', fig.cap="Visual comparison of Verification and Baseline spherical precision"}
if (params$has_baseline_comp == "Yes" && !is.null(params$ellipse_plot_path)) {
  cat("\n\n### Part II: Precision Comparison - Visualized Covariance Ellipses\n\n")
  
  knitr::include_graphics(params$ellipse_plot_path)
}
```

```{r, echo=FALSE, results='asis', fig.width=8, fig.height=3.75, fig.align='center', out.width="85%", fig.pos='H', fig.cap="Expected error ranges under current spherical precision"}
if (params$has_baseline_comp == "Yes" && !is.null(params$expectederror_plot)) {
  cat("### Part II: Plot of EER Values\n\n")
  print(params$expectederror_plot)
}
```

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$expected_errors)) {
  cat("### Part II: Complete Table of EER Values\n\n")
  print(knitr::kable(params$expected_errors, 
                     caption = "All 24 EER values",
                     booktabs = TRUE))
  cat("\n\n")
  statement <- paste0("These results were obtained from a Monte Carlo simulation using ", 
                      params$nIt_mcs, " iterations under random initialization seed configuration assignment ", 
                      params$seed_value, ".")
  cat(knitr::asis_output(statement))
  cat("\n\n")
}
```

\newpage

### METADATA

#### Residual plots 
Angular residuals are reported in arcseconds. Ranging residuals are reported in mm.

```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.align='center', out.width="75%", fig.pos='H', fig.cap="Residual plot"}
if (!is.null(params$resPlot_current)) {
  print(params$resPlot_current)
}
```

```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.align='center', out.width="75%", fig.pos='H', fig.cap="Residual plot (Baseline data)"}
if (params$has_baseline_comp == "Yes" && !is.null(params$resPlot_baseline)) {
  print(params$resPlot_baseline)
}
```

\newpage

### Current Data Metadata

#### TLS Data 
* **filename:** `r params$filename_TLS_test`
* **nickname:** `r params$dataname_test`
* **# of targets:** `r params$nT_test`
* **# of positions:** `r params$nP_test`
* **units:** `r params$TLS_UnitStatement`

#### Reference Lengths 
* **filename:** `r params$filename_reflengths`
* **units:** `r params$tapedata_summary`

```{r, echo=FALSE, results='asis'}
if (params$has_baseline_comp == "Yes" && !is.null(params$filename_TLS_baseline) && params$filename_TLS_baseline != "") {
  
  cat("### Baseline Data Metadata\n")
  cat("#### TLS Data\n")
  
  cat("* **filename:**", params$filename_TLS_baseline, "\n")
  cat("* **nickname:**", params$dataname_baseline, "\n")
  cat("* **# of targets:**", params$nT_baseline, "\n")
  cat("* **# of positions:**", params$nP_baseline, "\n")
  cat("* **units:**", params$baseline_TLS_UnitStatement, "\n")
  cat("\n")
  cat("#### Reference Lengths\n")
  cat("* **filename:**", params$filename_reflengths_baseline, "\n")
  cat("* **units:**", params$reflengths_baseline_summary, "\n")
  cat("\n")
}
```