---
title: "`r params$report_title`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  pdf_document:
header-includes:
#  - \usepackage{tcolorbox}
params:
  report_title: NA
  
  # Misc. stuff (file names/ user-specified names;)
  ## CURRENT DATA
  ##   TLS data - meta
  filename_TLStest: NA          # fn TLS data under test
  dataname_test: NA             # user-specified nickname for TLS data under test
  nT_test: NA                   # number of targets in Current TLS data
  nP_test: NA                   # number of positions in Current TLS data
  TLS_UnitStatement: NA         # unit statement for Current TLS data
  ##    Reference Length data
  filename_reflengths: NA       # fn Reference Lengths
  tapedata_summary: NA          # units for Reference Lengths (current)
  ##
  ## HISTORIC DATA
  ##    TLS data
  filename_TLShist: NA          # fn for historic TLS data
  dataname_base: NA             # user-specified nickname for Historic TLS data
  nT_base: NA                   # number of targets in Historic TLS data
  nP_base: NA                   # number of positions in Historic TLS data
  historicTLS_UnitStatement: NA # unit statement for historic TLS data
  ##    Reference Length data
  filename_reflengths_hist: NA  # fn for Historic reference lengths
  reflengths_hist_summary: NA   # unit statement for Historic reference lengths
  
  ## 
  ## RESULTS
  ##    Part I stuff
  length_summary: NA
  error_plot: NA                # Plot of the 24 length errors (Current data)
  error_table: NA               # Complete table of 24 length errors (current data)
  error_table_sub: NA           # subset table of length errors (current data) -- values that exceed threshold or top-3 values
  lengtherror_statements: NA
  ##    Part II stuff
  sd_test: NA
  p2_interpretation: NA
  Htest_details: NA               # Details from the hypothesis test
  sigmaHat_test: NA               # Est. covariance matrix from Current data
  sigmaHat_hist: NA               # Est. covariance matrix from Historic data
  
  ## HISTORIC COMPARISON (IF APPLICABLE)
  historic_comp: NA               # Binary 'Yes'/'No', indicating whether historic data was included
  ##    Part I
  length_summary_hist: NA         # summary statement ("x out of k historic length errors are...")
  error_table_hist: NA            # complete table of Historic length errors
  error_table_sub_hist: NA        # subtable of historic length errors
  errorPlot_hist: NA              # Historic Accuracy plot
  lengtherror_statements_hist: NA # details about the 6 Historic reference lengths
  ##    Part II
  basedata_sd: NA                 # Historic std deviations in residuals (vector of length 3)
  #Xcomb: NA                      # The data that will be used to render the data ellipse plot
  ellipse_plot_path: NA           # Path to the saved ellipse plot
  
  
  ## MCS stuff
  expected_errors: NA
  expectederrors_summary: NA
  expectederror_plot: NA          # Plot of EER values obtained from MCS
  seed_value: NA                  # random seed used for the MCS
  nIt_mcs: NA                     # number of MCS iterations (default = 3000)
  
  ## Data summaries/Notes
  notes: NA                       # User-given notes
  resPlot_current: NA             # Residual plot Current data
  resPlot_hist: NA                # Residual plot Historic data
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, echo=FALSE, results='asis'}
if (!is.null(params$notes) && nchar(trimws(params$notes)) > 0) {
  # 1. Escape special LaTeX characters first so they don't crash the PDF
  # This handles: %, $, &, #, _, { }
  safe_notes <- gsub("([#$%&_{}])", "\\\\\\1", params$notes)
  
  # 2. Convert manual line breaks (\n) into LaTeX paragraph breaks (\par)
  safe_notes <- gsub("\n", "\\\\par\n", safe_notes)
  
  # 3. Render the block
  cat("\n\\hrule\n") 
  cat("\\vspace{5pt}\n")
  cat("\\textbf{Report Notes:}\n")
  
  cat("\\begin{quote}\n")
  cat("\\small\\ttfamily\n") # Small, monospaced font
  cat(safe_notes)
  cat("\n\\end{quote}\n")
  
  cat("\\hrule\n")
  cat("\\vspace{10pt}\n")
} else {
  cat("\n\\hrule\n") 
  cat("\\vspace{5pt}\n")
  cat("\\textbf{Report Notes:}\n")
  
  cat("\\textit{No notes provided.}")
  
  cat("\\hrule\n")
  cat("\\vspace{10pt}\n")
}
```

# SUMMARY
## Part I - Accuracy
### Accuracy - Current Data
<!-- Statement of Part I errors (e.g., 3 out of 24 exceed...) -->
`r params$length_summary`
<!-- Print the subtable of errors, if necessary -->
```{r, echo = FALSE, results = 'asis'}
library(knitr)
library(kableExtra)
# 1. Check if the object is actually a data frame and has rows
if (is.data.frame(params$error_table_sub) && nrow(params$error_table_sub) > 0) {
  cat("Units in table are mm.\n")
  # 2. Use print() because results = 'asis' requires explicit output
  print(knitr::kable(params$error_table_sub, 
                    caption = "Length errors in Current data that exceed the given specification.",  
                     booktabs = TRUE))
  # 3. Add a couple of newlines to keep the LaTeX compiler happy
  cat("\n\n") 
} else {
  cat("")
}
```

<!-- PART I ERROR PLOT -->
```{r, echo=FALSE, fig.width=7, fig.height=3.25, fig.align='center', out.width="70%", fig.pos='!h', fig.cap="Length errors - Current data"}
if (!is.null(params$error_plot)) {
  params$error_plot
}
```
### Accuracy - Historic Data
<!-- If no historic objects are present, print 'No Historic Comparison was made -->
``` {r, echo=FALSE, results='asis'}
if(params$historic_comp=='No') {
  cat("No historic comparison was made.")
} 
```

<!-- Historic Accuracy summary statement -->
```{r, echo=FALSE, results='asis'}
if (!is.null(params$length_summary_hist)) {
  # Use ** for bold and cat() to print the raw text
  cat(params$length_summary_hist)
  
  # Add two newlines to ensure a proper paragraph break
  cat("\n\n")
}
```
<!-- Historic Accuracy subtable -->
```{r, echo = FALSE, results = 'asis'}
# 1. Check if the object is actually a data frame and has rows
if (is.data.frame(params$error_table_sub_hist) && nrow(params$error_table_sub_hist) > 0) {
  
  cat("Units in table are mm.\n")
  # 2. Use print() because results = 'asis' requires explicit output
  print(knitr::kable(params$error_table_sub_hist, 
                     caption = "Length errors in the Historic data that exceed the given specification.",  
                     #format = "latex", 
                     booktabs = TRUE))
  # 3. Add a couple of newlines to keep the LaTeX compiler happy
  cat("\n\n") 
} else {
  cat("")
}
```
<!-- If it exists, plot the historic Accuracy plot -->
<!-- PART I ERROR PLOT -->
```{r, echo=FALSE, fig.width=7, fig.height=3.25, fig.align='center', out.width="70%", fig.pos='!h', fig.cap="Length errors - Historic data"}
if (!is.null(params$errorPlot_hist)) {
  params$errorPlot_hist
}
```


## Part II - Precision
### Precision - Current Data
<!-- PART II: state the standard deviations -->
```{r, echo=FALSE, results='asis'}
if (!is.null(params$sd_test)) {
  # 1. Convert the HTML object to a character string
  sdtest_string <- as.character(params$sd_test)
  # 2. Replace <br> tags with LaTeX line breaks
  # We use quadruple backslashes because R escapes them for LaTeX
  sdtest_string_clean <- gsub("<br\\s*/?>", "\\\\par\n", sdtest_string)
  # 3. Clean up any other potential HTML artifacts
  sdtest_string_clean <- gsub("<.*?>", "", sdtest_string_clean) 
  # 4. Print to PDF
  cat(sdtest_string_clean)
  cat("\n\n\\par\n\n")
}
```
### Precision -- Historic Data
``` {r, echo=FALSE, results='asis'}
if(params$historic_comp=='No') {
  cat("No historic comparison was made.")
} 
```
<!-- Historical standard deviations -->
```{r, echo=FALSE, results='asis'}
if (params$historic_comp == "Yes" && !is.null(params$basedata_sd)) {
  cat("The historical standard deviation in the azimuth angle residuals is ", params$basedata_sd[1],
      " arcsec.\\par\n", sep = "")
  cat("The historical standard deviation in the elevation angle residuals is ", params$basedata_sd[2],
      " arcsec.\\par\n", sep = "")
  cat("The historical standard deviation in the ranging residuals is ", params$basedata_sd[3],
      " mm\\par\n", sep = "")

  cat("\n\n")
}
```
<!-- State the results of the hypothesis test, if applicable -->
```{r, echo=FALSE, results='asis'}
if (!is.null(params$p2_interpretation)) {
  cat("### Precision Comparison\n\n")
  cat(params$p2_interpretation)
  # Adding a newline ensures the next part of your report 
  # doesn't start on the same line
  cat("\n\n")
}
```

<!-- If the hypothesis test was significant, show the results of the MCS -->
<!-- EXPECTED ERRORS FROM MCS -->
```{r, echo=FALSE, results='asis'}
if(!is.null(params$expectederrors_summary)) {
  cat("### Effect of Current Precision on Length Errors\n\n")
## statement about what the EER values are
  cat("Since there is a statistically significance change in the precision, the effect of the instrument’s current spherical precision on the length measurements has been estimated using a Monte Carlo simulation. The “expected error range” (EER) value computed from this simulation is the range of error, for a given length and position, that is expected in the instrument’s measurement due to the current spherical precision.")
  cat("\n\n")
  ## summary of EER values
  cat(params$expectederrors_summary)
  cat("\n\n")
}
```
<!-- PLOT OF EXPECTED ERROR RANGE VALUES FROM MCS -->
```{r, echo=FALSE, fig.width=8, fig.height=3.75, fig.align='center', out.width="80%", fig.cap="Expected error ranges under Current spherical precision"}
if (!is.null(params$expectederror_plot)) {
  params$expectederror_plot
}
```

<!-- END THE 'SUMMARY' RESULTS -->
<!-- Draw horizontal line -->
\noindent\rule{\textwidth}{0.4pt}
\clearpage

## APPENDIX: DETAILED RESULTS

### Part I - Complete Table of Errors (Current data)
<!-- 1. 'params$error_table' is the data you sent from the app-->
<!-- 2. 'knitr::kable()' turns that data into a pretty table for PDF-->
```{r, echo=FALSE}
if (!is.null(params$error_table)) {
  knitr::kable(params$error_table, 
               caption = "Part I Length Errors (Current data)",
               booktabs = TRUE) 
} 
```
### Part I - Details on the six lengths and their reference values (Current data)
```{r, echo=FALSE, results='asis'}
if (!is.null(params$lengtherror_statements)) {
  for (item in params$lengtherror_statements$statement) {
    cat("* ", item, "\n")
  }
  cat("\n\n")
}
```
<!-- HISTORIC LENGTH ERRORS (TABLE)-->
```{r, echo=FALSE, results='asis'}
if (!is.null(params$error_table_hist)) {
  # This will now render as a proper Markdown header in the document font
  cat("\n#### Historic Accuracy - Complete table of Historic length errors\n\n")
  
  # results='asis' requires print() for kable to show up
  print(knitr::kable(params$error_table_hist, 
               caption = "Length errors (Historic data)",
               booktabs = TRUE)) 
}
```

```{r, echo=FALSE, results='asis'}
if (!is.null(params$lengtherror_statements_hist)) {
  cat("### Part I - Details on the six lengths and their reference values (Historic data)\n\n")
  for (item in params$lengtherror_statements_hist$statement) {
    cat("* ", item, "\n")
  }
  cat("\n\n")
}
```

### Current Precision - Estimated covariance matrix
<!-- COVARIANCE MATRIX (CURRENT DATA) -- always present-->
```{r, echo=FALSE}
# This chunk prints the object into a code box (the R console look)
if (!is.null(params$sigmaHat_test)) {
  print(round(params$sigmaHat_test,3))
}
```
<!-- COVARIANCE MATRIX (HISTORIC DATA) -- ONLY PRESENT IF HIST COMP WAS MADE-->
```{r, echo=FALSE, results='asis'}
# This chunk sends RAW text to the PDF to create a heading
if (!is.null(params$sigmaHat_hist)) {
  cat("#### Historic Precision - Estimated covariance matrix\n\n")
}
```
```{r, echo=FALSE}
# This chunk prints the object into a code box (the R console look)
if (!is.null(params$sigmaHat_hist)) {
  print(round(params$sigmaHat_hist,3))
}
```
**Coordinate Definitions:**

\begin{verse}
theta = azimuth angle (arcsec) \\
phi = elevation angle (arcsec) \\
r = ranging direction (mm)
\end{verse}

<!-- STATISTICAL DETAILS FROM THE HYPOTHESIS TEST -->
```{r, echo=FALSE, results='asis'}
# This chunk sends RAW text to the PDF to create a heading
if (!is.null(params$Htest_details)) {
  # Adding leading newlines here to ensure that this renders as a new section
  cat("\n\n### Precision Comparison - Hypothesis test details\n\n")
}
```
```{r, echo=FALSE}
# This chunk prints the object into a code box (the R console look)
if (!is.null(params$Htest_details)) {
  print(params$Htest_details)
}
```
<!-- Data ellipse plot -->
```{r, echo=FALSE, fig.align='center', results='asis', fig.width=5.5, fig.height=5.5, out.width="60%", fig.pos='!h', fig.cap="Visual comparison of Current and Historic spherical precision"}
if (!is.null(params$ellipse_plot_path)) {
  cat("\n\n### Precision Comparison - Data ellipse plots\n\n")
  knitr::include_graphics(params$ellipse_plot_path)
} 
```



<!-- COMPLETE MCS RESULTS -->
```{r, echo=FALSE, results='asis'}
if (!is.null(params$expected_errors)) {
  ## add the header
  cat("### Part II - Monte Carlo simulation complete results\n\n")
  # 1. Print the table first
  # Note: We use print() because kable needs to be explicitly pushed to the output in a loop/if block
  print(knitr::kable(params$expected_errors, 
               caption = "Part II MCS Results",
               booktabs = TRUE))
  # 2. Add a small vertical space
  cat("\n\n")
  # 3. Print the explanatory text
  # We use asis_output so the text matches the document font and handles the variables
  statement <- paste0("These results were obtained from a Monte Carlo simulation using ", 
                      params$nIt_mcs, " iterations and may be replicated using the seed ", 
                      params$seed_value, ".")
  cat(knitr::asis_output(statement))
  # 4. Add a final newline for spacing
  cat("\n\n")

} else {
  # If the data is missing, we print nothing at all
  cat("")
}
```

## METADATA
### Residual plots 
Angular residuals are reported in arcseconds. Ranging residuals are reported in mm.

<!-- RESIDUAL PLOT (CURRENT DATA) -->
```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.align='center', out.width="80%", fig.pos='!h', fig.cap="Residual plot (Current data)"}
if (!is.null(params$resPlot_current)) {
  print(params$resPlot_current)
}
```

<!-- RESIDUAL PLOT (HISTORIC DATA) -->
```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.align='center', out.width="80%", fig.pos='!h', fig.cap="Residual plot (Historic data)"}
if (!is.null(params$resPlot_hist)) {
  print(params$resPlot_hist)
}
```

\clearpage

### Current Data Metadata
#### TLS Data 
* **filename:** `r params$filename_TLStest`
* **nickname:** `r params$dataname_test`
* **# of targets:** `r params$nT_test`
* **# of positions:** `r params$nP_test`
* **units:** `r params$TLS_UnitStatement`

#### Reference Lengths 
* **filename:** `r params$filename_reflengths`
* **units:** `r params$tapedata_summary`

```{r, echo=FALSE, results='asis'}
# Check if a filename exists for the historic data
if (!is.null(params$filename_TLShist) && params$filename_TLShist != "") {
  
  cat("### Historic Data Metadata\n")
  cat("#### TLS Data\n")
  
  # We use a list format
  cat("* **filename:**", params$filename_TLShist, "\n")
  cat("* **nickname:**", params$dataname_base, "\n")
  cat("* **# of targets:**", params$nT_base, "\n")
  cat("* **# of positions:**", params$nP_base, "\n")
  cat("* **units:**", params$historicTLS_UnitStatement, "\n")
  # Add a final newline to separate this from whatever comes next
  cat("\n")
  cat("#### Reference Lengths\n")
  cat("* **filename:**", params$filename_reflengths_hist, "\n")
  cat("* **units:**", params$reflengths_hist_summary, "\n")
  cat("\n")
}
```

<!-- '`r params$dataname_test`' data read from file `r params$filename_TLStest`. Reference lengths corresponding to these data were read from file `r params$filename_reflengths`. -->